Post MCMCglmm analyses

### 2021-04-09 Analysis/06-post_mcmcglmm_analyses.Rmd
Updated analyses (added axes bits)

```{r}
source("../Functions/plot.ellipses.R")
source("../Functions/get.covar.R")
plot(morphdat[, c(1,2)], pch = 19, cex = 0.5,
     col = colour_vector[morphdat$clade],
     xlab = "PC1 (90.5%)",
     ylab = "PC1 (6.86%)")
plot.ellipses(model_phylo1_clade3, n = 100,
              centre = "none", add = TRUE, col = c("grey",colour_vector))
```

@@

```{r}
plot(morphdat[, c(1,2)], pch = 19, cex = 0.5,
     col = colour_vector[morphdat$clade],
     xlab = "PC1 (90.5%)",
     ylab = "PC1 (6.86%)")
plot.ellipses(model_phylo1_clade3, n = 100,
              centre = "level", add = TRUE, col = c("grey",colour_vector))
```
<!-- ## Get the ellipses centres
centres <- list(
    "phylo" = colMeans(morphdat[, c(1,2)]),
    "gulls" = colMeans(morphdat[which(morphdat$clade == "gulls"), c(1,2)]),
    "plovers" = colMeans(morphdat[which(morphdat$clade == "plovers"), c(1,2)]),
    "sandpipers" = colMeans(morphdat[which(morphdat$clade == "sandpipers"), c(1,2)]))

 -->

@@

```{r}

```

>>>>

```{r}
source("../Functions/plot.ellipses.R")
source("../Functions/get.covar.R")

## Selecting 100 random covariance matrices from the MCMCglmm
covar_matrices <- get.covar(model_phylo1_clade3,
                            n = 100,
                            simplify = FALSE)

## Plotting the results
plot(morphdat[, c(1,2)], pch = 19, cex = 0.5,
     col = colour_vector[morphdat$clade],
     xlab = "PC1 (90.5%)",
     ylab = "PC1 (6.86%)")
plot.ellipses(covar_matrices, centre = "none",
              col = c("grey",colour_vector),
              add = TRUE)
```

@@

```{r}
plot(morphdat[, c(1,2)], pch = 19, cex = 0.5,
     col = colour_vector[morphdat$clade],
     xlab = "PC1 (90.5%)",
     ylab = "PC1 (6.86%)")
plot.ellipses(covar_matrices, centre = "level",
              col = c("grey",colour_vector),
              add = TRUE)
```

@@

```{r}
source("../Functions/get.axes.R")
## Get all the phylo main axes
level_centred_major_axes <- get.axes(covar_matrices, centre = "level")
uncentered_major_axes <- get.axes(covar_matrices, centre = "none")
```

And this is what it looks like for the uncentred ones:

```{r}
plot(morphdat[, c(1,2)], pch = 19, cex = 0.5,
     col = colour_vector[morphdat$clade],
     xlab = "PC1 (90.5%)",
     ylab = "PC1 (6.86%)")
plot.ellipses(covar_matrices, centre = "none",
              col = c("grey",colour_vector),
              add = TRUE)
plot.all.axes(uncentered_major_axes,
         col = c("grey",colour_vector),
         add = TRUE)
```

And for the centred ones:

```{r}
plot(morphdat[, c(1,2)], pch = 19, cex = 0.5,
     col = colour_vector[morphdat$clade],
     xlab = "PC1 (90.5%)",
     ylab = "PC1 (6.86%)")
plot.ellipses(covar_matrices, centre = "level",
              col = c("grey",colour_vector),
              add = TRUE)
plot.all.axes(level_centred_major_axes,
         col = c("grey",colour_vector),
         add = TRUE)
```

Or without all the points n stuff

```{r, fig.height = 4, fig.width = 8}
par(mfrow = c(1,2))
plot.all.axes(uncentered_major_axes,
         col = c("grey",colour_vector),
         add = FALSE, main = "Major axes (un-centred)")
plot.all.axes(uncentered_major_axes,
         col = c("grey",colour_vector),
         add = FALSE, main = "Major axes (level-centred)")
```
